Thermodynamic fragments in magic state theories

### 2020-12-16 magic_paper.tex
Question on mana bound. Things to be expanded on for the thermal fragment analysis.

Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain a \nick{lower} bound on the unital fragment distillation rate $R=n/n'$ given by
\begin{equation}
R \geq \frac{\ln (3-4 \epsilon)}{\ln 3},
\end{equation}
which holds for all finite $n$. 
In comparison, the bound from mana gives 
\begin{equation}
	R_{\rm{mana}} \geq \frac{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)}{\ln \frac{5}{3}},
\end{equation}
a threshold which is lower/looser than the one provided by majorization for all $\epsilon > 0$.

\ddd{[This is good, and the bound coming from the first elbow seems very easy to obtain. Going forward:
\begin{enumerate}
\item Does the ``last elbow'' give the same bound? Is it as simple?
\item Numerically is this about as good as it gets from majorization?
\item How does this rate compare with existing literature?
\end{enumerate}
If this bound is better than existing literature then great. I suspect not though. However, remember the core message of our work is that we're ``incorporating physical restrictions'' into the magic analysis. Given this, one thing that would round the paper off could be if we re-played the ``first elbow'' bound for some non-trivial temperature. Meaning: choose a ``nice'' Hamiltonian and compute the first elbow constraint via the thermo-majorization distortion of the Wigner components. This would then give us something clearly new -- namely a bound with temperature dependence! People would find this interesting since nothing like it exists yet.}

@@

Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}.
The Wigner distribution of any thermal state $\gamma_\beta$ always consists of strictly positive components,
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
so pre-order $\prec_{\gamma_\beta}$ is well defined.

@@

However, higher copies are not sorted, for example
\begin{equation}
	\begin{split}
	\W{\gamma_\beta\too{2}} = \frac{1}{9\Z_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_1 + E_0)}}^3, \overbrace{e^{-\beta 2E_1}}^3, \overbrace{e^{-\beta (E_1 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_2 + E_0)}}^3, \overbrace{e^{-\beta (E_2 + E_1)}}^3, \overbrace{e^{-\beta 2E_2}}^3}^3 \Bigg).
	\end{split}
\end{equation}
For the Strange state we have
\begin{equation}
	\begin{split}
	\W{\noisys(\epsilon)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^2}^1, \overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^{8}, \\
	&\overbrace{\overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^1, \overbrace{\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^2}^8}^8,  \Bigg).
	\end{split}
\end{equation}
\nick{We need to sort the distributions $\W{\gamma_\beta\too{2}}, \W{\noisys(\epsilon)\too{2}}$, so that the vector
\begin{equation}
	\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\noisys(\epsilon)\too{2}})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{81}}{(\W{\sigma})_{81}} \right)^T,
\end{equation}
is in decreasing order, i.e. $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
Then, we need to generalise for any number of copies $n$}

>>>>

Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain a upper bound on the unital fragment distillation rate $R=n'/n$ given by
\begin{equation}
R \leq \frac{\ln 3}{\ln (3-4 \epsilon)},
\end{equation}
which holds for all finite $n$. 
In comparison, the bound from mana gives 
\begin{equation}
	R_{\rm{mana}} \leq \frac{\ln \frac{5}{3}}{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)},
\end{equation}
a threshold which is looser than the one provided by majorization for all $\epsilon > 0$. For example, for $\epsilon = 0.4$ we obtain $R\le 3.27 $ while the mana bound gives $R_{\rm{mana}} \le 1.89$. \ddd{[Am I making some mistake here?? Mana does better according to these numbers? Does it only do better for a region of $\epsilon$ values? Perhaps plot the functions together.]}

\ddd{[Going forward:
\begin{enumerate}
\item Does the ``last elbow'' give the same bound? Is it as simple?
\item Numerically is this about as good as it gets from majorization?
\item How does this rate compare with existing literature?
\end{enumerate}
If this bound is better than existing literature then great. I suspect not though. However, remember the core message of our work is that we're ``incorporating physical restrictions'' into the magic analysis. Given this, one thing that would round the paper off could be if we re-played the ``first elbow'' bound for some non-trivial temperature. Meaning: choose a ``nice'' Hamiltonian and compute the first elbow constraint via the thermo-majorization distortion of the Wigner components. This would then give us something clearly new -- namely a bound with temperature dependence! People would find this interesting since nothing like it exists yet.}

@@

Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}. \ddd{[Completely vital. What Hamiltonian are you choosing? Note you can choose it to make life easy for yourself. E.g. $H=Z$ for example.]}
The Wigner distribution of any thermal state $\gamma_\beta$ always consists of strictly positive components,
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
so pre-order $\prec_{\gamma_\beta}$ is well defined. \ddd{[Not clear where this equation comes from.]}

@@

However, higher copies are not sorted, for example
\begin{equation}
	\begin{split}
	\W{\gamma_\beta\too{2}} = \frac{1}{9\Z_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_1 + E_0)}}^3, \overbrace{e^{-\beta 2E_1}}^3, \overbrace{e^{-\beta (E_1 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_2 + E_0)}}^3, \overbrace{e^{-\beta (E_2 + E_1)}}^3, \overbrace{e^{-\beta 2E_2}}^3}^3 \Bigg).
	\end{split}
\end{equation}
\ddd{[Definitely impressed by this Latexing...but perhaps just give the multiplicities and spectrum values. I.e. ``(blah) with multiplicity (blah) and ...'']} For the Strange state we have
\begin{equation}
	\begin{split}
	\W{\noisys(\epsilon)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^2}^1, \overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^{8}, \\
	&\overbrace{\overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^1, \overbrace{\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^2}^8}^8,  \Bigg).
	\end{split}
\end{equation}
\nick{We need to sort the distributions $\W{\gamma_\beta\too{2}}, \W{\noisys(\epsilon)\too{2}}$, so that the vector
\begin{equation}
	\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\noisys(\epsilon)\too{2}})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{81}}{(\W{\sigma})_{81}} \right)^T,
\end{equation}
is in decreasing order, i.e. $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
Then, we need to generalise for any number of copies $n$}
